Learning Reusable Components for Neurally--Guided Bayesian Program Learning

### 2018-05-12 nips_2018.tex
listed primitives

The architecture of $q$ depends upon the domain.
For domains with sequential structure like strings and lists,
we use an RNN to encode each input/output example.
For domains with fixed-dimensionality inputs/outputs we use a multilayer perceptron.
We MaxPool across all of the input/output examples. See Supplement for details.

@@

\section{Experiments}
We first present our experimental results qualitatively,
illustrating the learned DSLs.
We then show quantitative results (Sec.~\ref{quantitative})
comparing \system with lesioned versions
of our model that are analogous to prior work.

\subsection{Symbolic Regression}\label{regressionSection}
We show how to use \system to infer programs containing both discrete
structure and continuous parameters. The high-level idea is to write programs with unspecified real-valued parameters, and to fit those parameters by differentiating through the program
and optimizing using gradient descent.
We task our model
with solving 200 symbolic regression problems, each either a polynomial of
degree 1 to 4 or a rational function.
The recognition model is a convolutional network that observes an image
of the target function's graph (Fig.~\ref{functions}) --
visually, different kinds of polynomials and rational functions
produce different kinds of graphs,
and so the recognition model must learn to
look at a graph and predict what kind of function best explains it.
\begin{wrapfigure}{r}{0.3\textwidth} \newcommand{\functionSize}{0.75cm}
  \includegraphics[width = \functionSize]{figures/functions/0.png}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/207.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/303.png}\\  
  \includegraphics[width = \functionSize]{figures/functions/402.png}
  \includegraphics[width = \functionSize]{figures/functions/415.png}
  \includegraphics[width = \functionSize]{figures/functions/426.png}
  \includegraphics[width = \functionSize]{figures/functions/597.png}
  \includegraphics[width = \functionSize]{figures/functions/591.png}
  \caption{Recognition model input for symbolic regression. While the DSL learns subroutines for rational functions \& polynomials, the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines is appropriate for explaining the observation.}\label{functions}
  \end{wrapfigure}

@@

\subsection{String Editing}\label{textSection}
Synthesizing programs that manipulate strings is a classic problem in the
programming languages and AI literatures~\cite{menon2013machine,lau2001programming},
and algorithms that learn string editing programs ship in Microsoft Excel~\cite{gulwani2011automating}.
However, this prior work presumes a ready-made DSL,
expertly crafted to suit string editing.
We show in this experiment that we can instead start out with a
less specialized set of primitives -- close to the string methods provided by Python --
and recover many of the higher-level building blocks that have made these
other system successful.
Tbl.~\ref{textPrimitives} (top) lists the primitive functions provided to \systemEnding.
Absent are any routines for searching for characters, extracting substrings,
or replacing one character with another.
Instead, we provide list/string indexing primitives (\code{slice}, \code{nth}),
basic arithmetic, and functions for splitting a string into a list (\code{split})
or turning a list into a string (\code{join}).
We automatically generated  600 string editing tasks  with 4 input/output examples each (Fig.~\ref{exampleTextProblem}). %, split  75/25 train/test.
At first, \system cannot find any correct programs for most of the tasks.
After three wake/sleep iterations,
it assembles a DSL (Tbl.~\ref{textPrimitives}, bottom) that lets it rapidly explore the space of programs and find solutions to
all of the tasks.

@@

\subsection{List Functions}
Synthesizing programs that manipulate data structures is
a widely studied problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of
learning functions that manipulate lists.
We created 225 Lisp-style list manipulation tasks,
each with 15 input/output examples (Tbl.~\ref{listexamples}).
Our data set is challenging along two dimensions:
many of the functions are very complicated,
and the agent must learn to solve these complicated problems from only 225 tasks.

>>>>

%% The architecture of $q$ depends upon the domain.  For domains with
%% sequential structure like strings and lists, we use an RNN to encode
%% each input/output example.  For domains with fixed-dimensionality
%% inputs/outputs we use a multilayer perceptron.  We MaxPool across all
%% of the input/output examples. See Supplement for details.

@@

\section{Experiments}
%% We first present our experimental results qualitatively,
%% illustrating the learned DSLs.
%% We then show quantitative results (Sec.~\ref{quantitative})
%% comparing \system with lesioned versions
%% of our model that are analogous to prior work.

\subsection{Symbolic Regression}\label{regressionSection}
\begin{wrapfigure}{r}{0.3\textwidth} \newcommand{\functionSize}{0.75cm}
  \includegraphics[width = \functionSize]{figures/functions/0.png}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/207.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/303.png}\\  
  \includegraphics[width = \functionSize]{figures/functions/402.png}
  \includegraphics[width = \functionSize]{figures/functions/415.png}
  \includegraphics[width = \functionSize]{figures/functions/426.png}
  \includegraphics[width = \functionSize]{figures/functions/597.png}
  \includegraphics[width = \functionSize]{figures/functions/591.png}
  \caption{Recognition model input for symbolic regression. While the DSL learns subroutines for rational functions \& polynomials, the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines is appropriate for explaining the observation.}\label{functions}
  \end{wrapfigure}We show how to use \system to infer programs containing both discrete
structure and continuous parameters. The high-level idea is to write programs with unspecified real-valued parameters, and to fit those parameters by differentiating through the program
and optimizing using gradient descent.
We task our model
with solving 200 symbolic regression problems, each either a polynomial of
degree 1 to 4 or a rational function.
The recognition model is a convolutional network that observes an image
of the target function's graph (Fig.~\ref{functions}) --
visually, different kinds of polynomials and rational functions
produce different kinds of graphs,
and so the recognition model can learn to
look at a graph and predict what kind of function best explains it.

@@

\subsection{Programs that manipulate sequences}\label{sequences}
We apply \system to text editing (Section~\ref{textSection}) and list processing (Section~\ref{listSection})  problems.
For both these domains we initially provide the system with a generic
minimal set of programming primitives,
and use a bidirectional GRU~\cite{cho2014learning} for the recognition model.
The initial set of primitives includes \code{fold}, \code{unfold}, \code{if}, \code{map}, \code{length}, \code{=}, \code{+}, \code{-}, \code{0}, \code{1}, \code{cons}, \code{car}, \code{cdr}, \code{nil}, and \code{is-nil}.

\subsubsection{String Editing}\label{textSection}
Synthesizing programs that manipulate strings is a classic problem in the
programming languages and AI literatures~\cite{menon2013machine,lau2001programming},
and algorithms that learn string editing programs ship in Microsoft Excel~\cite{gulwani2011automating}.
However, this prior work presumes a ready-made DSL,
expertly crafted to suit string editing.
We show \system can instead start out with generic primitives
and recover many of the higher-level building blocks that have made these
other system successful.
We automatically generated  600 string editing tasks  with 4 input/output examples each (Fig.~\ref{exampleTextProblem}). %, split  75/25 train/test.
At first, \system cannot find any correct programs for most of the tasks.
It assembles a DSL (Tbl.~\ref{textPrimitives}) that lets it rapidly explore the space of programs and find solutions to
all of the tasks.

@@

\subsubsection{List Functions}\label{listSection}
Synthesizing programs that manipulate data structures is
a widely studied problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of
learning functions that manipulate lists.
We created 225 Lisp-style list manipulation tasks,
each with 15 input/output examples (Tbl.~\ref{listexamples}).
Our data set is challenging along two dimensions:
many of the functions are very complicated,
and the agent must learn to solve these complicated problems from only 225 tasks.
